% vim:ft=tex:
%
\documentclass{letter}

\usepackage[T1]{fontenc}
\usepackage{todonotes}
\usepackage{siunitx}

\signature{Tayler Mulligan}
\address{858 Beatty St. \\ Vancouver, BC \\ V6B 1C1}
\begin{document}

\begin{letter}{Ms. Rhonda Korol \\ Co-op Coordinator \\ Faculty of Engineering
\\ University of Victoria \\ P.O. Box 1700 \\ Victoria, B.C. \\ V8W 2Y2}
\opening{Dear Ms. Rhonda Korol:}

Please accept the accompanying Work Term report entitled "Implementing
metrics on a real-time data processing pipeline."

This report was written on my second work term as a 3B Electrical student
working for Avigilon Corp. Avigilon provides security solutions in the form of
networked security cameras and viewing software. The contents of this report
detail the implementation of metrics for a real-time processing pipeline. This
pipeline is used in the security camera server where-ever a stream requires
real-time processing. The addition of metrics aids in debugging when using this
processing framework.

Throughout the term I was exposed to new topics regarding both embedded software
development and the wider realm of the security sector. I learned about working
on large codebases, supporting multiple platforms and products, embedded device
imaging, embedded Linux development, and general embedded software development.
I hope this new information and experience will be beneficial in furthering my career.

I would like to the thank my team lead Patrick Beaulieu, and team members
Olivier Thomas, Larry Zhan, and Jiawei Huang for all the assistance and
guidance. I would also like to thank my manager Ken Jessen for giving me the
opportunity to work with this team.

\closing{Sincerely,}

\end{letter}
\end{document}
